\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2023-11-14 doc/USER_MANUAL/04_creating_databases.tex
adds support for MOVIE_VOLUME_STRESS flag and output

\noindent {\bf $\bullet$ Simulation setup}
\begin{description}
\item [{\texttt{SIMULATION\_TYPE}}] is set to 1 for forward simulations,
2 for adjoint simulations (see Section \ref{sec:Adjoint-simulation-finite})
and 3 for kernel simulations (see Section \ref{sec:Finite-Frequency-Kernels}).
\item [{\texttt{SAVE\_FORWARD}}] is only set to \texttt{.true.} for a forward
simulation with the last frame of the simulation saved, as part of
the finite-frequency kernel calculations (see Section \ref{sec:Finite-Frequency-Kernels}).
For a regular forward simulation, leave \texttt{SIMULATION\_TYPE}
and \texttt{SAVE\_FORWARD} at their default values.
\item [{\texttt{UTM\_PROJECTION\_ZONE}}] UTM projection zone in
which your model resides, only valid when \texttt{SUPPRESS\_UTM\_PROJECTION} is \texttt{.false.}.
\item [{\texttt{SUPPRESS\_UTM\_PROJECTION}}] set to be \texttt{.false.}
when your model range is specified in the geographical coordinates,
and needs to be \texttt{.true.} when your model is specified in a
cartesian coordinates. \noun{UTM projection zone in which your simulation
region resides.}
\item [{\texttt{NPROC}}] The number of MPI processors, each one is assigned
one slice of the whole mesh.
\item [{\texttt{NSTEP}}] The number of time steps of the simulation. This
controls the length of the numerical simulation, i.e., twice the number
of time steps requires twice as much CPU time. This feature is not
used at the time of generating the distributed databases but is required
for the solver, i.e., you may change this parameter after running
\texttt{xgenerate\_databases}.
\item [{\texttt{DT}}] The length of each time step in seconds. This feature
is not used at the time of generating the distributed databases but
is required for the solver. Please see also Section~\ref{sec:Choosing-the-Time-Step}
for further details.
\end{description}

@@

if you want to save the stress tensor for the volume movie. To activate this option, \texttt{MOVIE\_VOLUME} must be \texttt{.true.}. Please note that this option will generate huge output because it will save six independent stress tensor components in the entire volume. This option is currently implemented only for the viscoelastic simulations.

@@

\item [\texttt{ADIOS\_ENABLED}] Turn this flag on to enable ADIOS. If set to \texttt{.false.}, subsequent ADIOS
parameters will not be considered.
\item [\texttt{ADIOS\_FOR\_DATABASES}] Turn this flag on to use ADIOS for xmeshfem3D output and
xgenerate\_database input.
\item [\texttt{ADIOS\_FOR\_MESH}]  Turn this flag on to use ADIOS for generated databases.
\item [\texttt{ADIOS\_FOR\_FORWARD\_ARRAYS}] Turn this flag on to read and write forward arrays using ADIOS.
\item [\texttt{ADIOS\_FOR\_KERNELS}] Turn this flag on to produce ADIOS kernels that can later be visualized with the ADIOS version of combine\_vol\_data.
\end{description}
There are quite a few more parameters to change the default setup of your runs. Please check the comments in the \texttt{DATA/Par\_file} directly for further explanations.\newline

>>>>

\noindent {\bf $\bullet$ Simulation setup}
\begin{description}
\item [{\texttt{SIMULATION\_TYPE}}] is set to 1 for forward simulations,
2 for adjoint simulations (see Section \ref{sec:Adjoint-simulation-finite})
and 3 for kernel simulations (see Section \ref{sec:Finite-Frequency-Kernels}).
\item [{\texttt{SAVE\_FORWARD}}] is only set to \texttt{.true.} for a forward
simulation with the last frame of the simulation saved, as part of
the finite-frequency kernel calculations (see Section \ref{sec:Finite-Frequency-Kernels}).
For a regular forward simulation, leave \texttt{SIMULATION\_TYPE}
and \texttt{SAVE\_FORWARD} at their default values.
\item [{\texttt{UTM\_PROJECTION\_ZONE}}] UTM projection zone in
which your model resides, only valid when \texttt{SUPPRESS\_UTM\_PROJECTION} is \texttt{.false.}.
\item [{\texttt{SUPPRESS\_UTM\_PROJECTION}}] set to be \texttt{.false.}
when your model range is specified in the geographical coordinates,
and needs to be \texttt{.true.} when your model is specified in a
cartesian coordinates. \noun{UTM projection zone in which your simulation
region resides.}
\item [{\texttt{NPROC}}] The number of MPI processors, each one is assigned
one slice of the whole mesh.
\item [{\texttt{NSTEP}}] The number of time steps of the simulation. This
controls the length of the numerical simulation, i.e., twice the number
of time steps requires twice as much CPU time. This feature is not
used at the time of generating the distributed databases but is required
for the solver, i.e., you may change this parameter after running
\texttt{xgenerate\_databases}.
\item [{\texttt{DT}}] The length of each time step in seconds. This feature
is not used at the time of generating the distributed databases but
is required for the solver. Please see also Section~\ref{sec:Choosing-the-Time-Step}
for further details.
\item [{\texttt{LTS\_MODE}}] Turning this flag on will use a local-time stepping scheme for the Newmark time scheme.
It will re-distribute the mesh partitioning to balance out elements with similar local-time step sizes.
This feature can help improve the time-to-solution when the mesh contains elements of various sizes,
in particular when the mesh contains only a few very small elements that would limit the global time step size.

@@

if you want to save the stress tensor for the volume movie.
To activate this option, \texttt{MOVIE\_VOLUME} must be \texttt{.true.}.
Please note that this option will generate huge outputs, because it will save six independent stress tensor components in the entire volume.
This option is currently implemented only for the viscoelastic simulations.

@@

%% ADIOS
\item [\texttt{ADIOS\_ENABLED}] Turn this flag on to enable ADIOS. If set to \texttt{.false.}, subsequent ADIOS
parameters will not be considered.
\item [\texttt{ADIOS\_FOR\_DATABASES}] Turn this flag on to use ADIOS for xmeshfem3D output and
xgenerate\_database input.
\item [\texttt{ADIOS\_FOR\_MESH}]  Turn this flag on to use ADIOS for generated databases.
\item [\texttt{ADIOS\_FOR\_FORWARD\_ARRAYS}] Turn this flag on to read and write forward arrays using ADIOS.
\item [\texttt{ADIOS\_FOR\_KERNELS}] Turn this flag on to produce ADIOS kernels that can later be visualized with the ADIOS version of combine\_vol\_data.

%% HDF5
\item [\texttt{HDF5\_ENABLED}] Turn this flag on to enable HDF5 file I/O. If set to \texttt{.false.}, subsequent HDF5
parameters will not be considered.
\item [\texttt{HDF5\_FOR\_MOVIES}] Turn this flag on to use HDF5 format for movie outputs.
\item [\texttt{HDF5\_IO\_NODES}] Setting this number >0 will allocate additional MPI processes specifically to handle
the HDF5 file I/O in an asynchronous way.

\end{description}
There are quite a few more parameters to change the default setup of your runs. Please check the comments in the \texttt{DATA/Par\_file} directly for further explanations.\newline
